
---
title: "SLUcolors"
output:
  rmarkdown::html_vignette: default
  pdf_document: default
vignette: >
  %\VignetteIndexEntry{SLUcolors}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

SLUcolors is a R a package that tries to make the use of officialy defined SLU-colors in R easy. The use of
the SLU color palette can give a coherant SLU-look presentations, fact-sheets and other communication,
especially combined with official templates for PowerPoint etc. For more info see [https://internt.slu.se/en/support-services/administrative-support/communication/brand-guidelines/visual-identity/slu-colours/palette/](https://internt.slu.se/en/support-services/administrative-support/communication/brand-guidelines/visual-identity/slu-colours/palette/)

# Installation
The easiest way to install package *SLUcolors* is to use *remotes::install_github("kagervall/SLUcolors", build_vignettes = TRUE)* from package *remotes*.
```{r install, eval=FALSE}
if (!require(remotes)) {
  install.packages(remotes)
}
remotes::install_github("kagervall/SLUcolors")
```

# Getting color palettes

The function `SLUpalette()` is used to get variants of the SLU color palette (or all 26 available colors).
A color palette is a vector of color codes that can be used in other functions. The vector returned by
`SLUpalette()` is named using the swedish names of the color as defined by "Communication & marketing".
SLUpalette(palette) takes one parameter, palette, that can be either a character or an integer. When palette
is a character the allowed strings are: "red", "green", "blue", "yellow", "grey" or "all", this will return columns from the official palette. When palette is an integer it can take the values 1 to 5, this will return rows from the official palette.

The package also includes a color palette suitable for categorical data optimized for colorblind individuals. The palette includes 5 colors from the
`Wong` (ref?) palette and the colors are not "official" SLU colors. This palette is returned by the call `SLUpalette("wong_234516")`. If/when a categorical palette using official colors is defined the the `wong_234516`
will be deprecated.

```{r example1}
library(colorspace) # For swatchplot()
library(SLUcolors)

# Get colomn from the palette = "Shades of color"
reds <- SLUpalette("red") # Get a palette with 5 "Shades of red"
reds # The returned value is a (by default) named vector.
# Get rows from palette 
row1 <- SLUpalette(1)
row2 <- SLUpalette(2)
row3 <- SLUpalette(3)
row4 <- SLUpalette(4)
row5 <- SLUpalette(5)
swatchplot("Deep 1" = row1,
           "Deep 2" = row2,
           "Clear1" = row3,
           "Clear2" = row4,
           "Light" = row5,
           "wong" = SLUpalette("wong_234516"))

```

# Base graphic
Here are some simple examples of how to use the SLU colors in base plot.
```{r example2}
h <- matrix(data = 1:9, nrow = 3, byrow = TRUE)
# Bar plot using the green palette for the bars. Reverse the palette to get the lightest colors 
barplot(h, col = rev(SLUpalette("green")), main = "Palette green")

# Bar plot using row 5 (light colors) from the palette. 
barplot(h, col = SLUpalette(5), main = "Row 5 (Light)")
```



# Theme for ggplot2
The function *theme_SLU(palette, dark)* returns a theme that can be applied to a plot created with ggplot2. When the parameter *dark* is *TRUE* (the default) the theme will have a dark background and light foreground. Set *dark* to *FALSE* to get a light background and dark foreground. This function probably work best with the color based ("red", "green", "blue" or "yellow") themes.
The goal of the theme is to get a plot that blends well with the official SLU templates for PowerPoint. Feedback on the design is welcome as I am a decent programmer and a lousy designer.

```{r example3, fig.height=3, fig.width=5}
library(ggplot2)
p1 <- ggplot(iris, mapping = aes(x = Sepal.Width, y = Sepal.Length))
  
p1 + labs(title = "Red on green") +
  geom_point(color = SLUpalette("red")["Hallon"]) +
  theme_SLU("green")

cols <- SLUpalette(3)
names(cols) <- NULL # Must remove names for scale_color_manual() 
p1 +  labs(title = "Light blue, grouped by species") +
  geom_point(aes(colour = Species)) +
  scale_color_manual(values = cols) +
  theme_SLU("blue", dark = FALSE)
```

# Wong palette
Simple example using `wong_234516` palette with `ggplot2`

```{r example4, fig.height=3, fig.width=5}
p2 <- ggplot(mtcars, mapping = aes(x = factor(carb)))
p2 + geom_bar(stat = "count", fill = SLUpalette("wong_234516")) + xlab("Carburator type")

```
